---
title: "Cabbages"
author: "Sakana Uthayasegar"
date: "Summer 2023 "
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H(O)$: There is no difference in the vitamin C content of cabbages based on cultivation techniques.

$H(A)$: There is a difference in vitamin C content of cabbages based on cultivation techniques. 

# Methods

The response variable is numerical. The input variable is categorical. this is a num~cat. 

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

```{r}
favstats(VitC~Cult,data=veggy)
```
The table shows that cultivation method c52 has higher vitamin c content than c39. C52 shows average of 13mg.

### Graphical Descriptive Results

```{r}
plot(VitC~Cult,data=veggy)
```
Graph shows C52 is higher in Vit C content higher than C39.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results




<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```
0.00000003045 number is so small, that I reject the null hypothesis. The difference is seen in Vitamin C, C52 is better.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

There is a significant difference in Vitamin C, between C39 and C52. Based on T test, i8t is found that C52 was better with Vitamin C, C52 is better. 

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
